Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-18 paper/sections/related-work.tex
[ paper ] lots of grammar fixes.

Kanso and Setzer~\cite{kanso2016light} integrate the propositional
fragment of \name{EProver} in \Agda. In this work, the authors
translate automatically propositional logic problems written in \Agda
to \TPTP problems. By calling an external wrapper of the ATP, this
tool gets a \TSTP derivation. The tool parses the \name{EProver}
derivation and outputs \Agda code.
We able to say their proof-reconstruction is almost
similar as the approach presented in Section~\ref{ssec:workflow}.
Nevertheless, Kanso and Setzer aim to justify some of the inference
rules by using propositional semantics instead of an only syntactic
treatment as we did in this work.

>>>>

Kanso and Setzer~\cite{kanso2016light} integrate the propositional
fragment of \name{EProver} in \Agda. In this work, the authors
translate automatically propositional logic problems written in \Agda
to \TPTP problems. By calling an external wrapper of the ATP, this
tool gets a \TSTP derivation. The tool parses the \name{EProver}
derivation and outputs \Agda code.
We are able to say their proof-reconstruction is almost
similar as the approach presented in Section~\ref{ssec:workflow}.
Nevertheless, Kanso and Setzer aim to justify some of the inference
rules by using propositional semantics instead of only syntactic
treatment as shown above.
